### 2017-01-11 paper/evaluation.tex
pass in RQ2 (not done)

To evaluate the distribution of time cost, we analyzed the execution
time of each test case from the \numMedLong{} subjects from the
\longg{} and \medg{} groups identified in Section~\ref{sec:rqA}. We
are interested to know whether most of the execution cost of a subject
is dominated by a small subset of test cases or if the cost is nearly
equally distributed. For each subject we calculated the relative
standard deviation of the test cases: we collected the elapsed time of
each individual test, calculated the standard deviation, and divided
by the mean. \Jbc{I need to clarify the relationship
"well/bad-balanced" regression test and relative standard deviation}

>>>>

Section~\ref{sec:rqA} showed that medium and long-running projects are
not uncommon; they account to nearly \percentMedLongRunning{} of the
\numSubjsTotal{} projects we analyzed.  A key factor to determine if
low-level parallelism will be effective to speedup test execution is
to identify whether or not a small fraction of tests dominate test
suite execution time.  If that is the case, it is unlikely that test
suite parallelization will help as a test artifact is the smallest
working unit in test frameworks (see Section~\ref{sec:frameworks}).
Ideally, one would hope that time is distributed uniformly across
tests in the suite.

%% We are interested to know whether
%% most of the execution cost of a subject is dominated by a small subset
%% of test cases or if the cost is nearly equally distributed.

To evaluate the distribution of time, we analyzed the execution time
for the \numMedLong{} projects from the \longg{} and \medg{} groups
(see Section~\ref{sec:rqA}).

For each subject we calculated the
relative standard deviation of the test cases: we collected the
elapsed time of each individual test, calculated the standard
deviation, and divided by the mean. \Jbc{I need to clarify the
  relationship "well/bad-balanced" regression test and relative
  standard deviation}
